Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-01 paper/v1.0/sections/4_floquet_fermi_golden.tex
Add section 3 of paper

In this section we are going to derive the Floquet Fermi goldern rule for previously derived quantum Floquet states using $t-t'$ formalism \cite{bruus04}.

>>>>

In Ref. \cite{wackerl20} Floquet Fermi golden rule has been introduced as a method to analyse transport propeties in dressed quantum systems. However, this theory has not been applied for a dressed quantum Hall system and to identify magnetotransport properties in our system we use Floquet Fermi golden rule.
With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and using Floquet states derived in Eq.~(\ref{eq_12}) we can derive Floquet Fermi golden rule for our considered quantum Hall system as
\begin{widetext}
\begin{equation} \label{4.65}
  \begin{aligned}
    \qty(\frac{1}{\tau(\varepsilon,k_x)})^{ll'}_{N} =
    \frac { \eta_{imp}^2 L_x^2 \hbar V_{imp}}{\qty(eB)^2}
    \delta(\varepsilon - \varepsilon_{N})
    \int_{-\infty}^{\infty} d k_1
    &
    J_l\qty(\frac{g\hbar}{eB}[{k}_x - k_1])
    J_{l'}\qty(\frac{g\hbar}{eB}[{k}_x - k_1]) \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} dk_2 \;
    {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2.
  \end{aligned}
\end{equation}
\end{widetext}
